\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-06-11 manuscript/manuscript.tex
addressed comments

Automatic block size selection tends to yield larger block sizes than our
fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
negative or very strong positive dependence it systematically produces
block sizes that are excessively large, sometimes as large as or larger
than $n$. Figure~\ref{fig:block_dist} illustrates the typical behavior by
showing the distribution of block sizes selected by \citet{politis2004automatic}
for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
block sizes exceeding $n$ across varying levels of dependence and sample sizes.
The selection of block sizes larger than $n$ occurs systematically under strong
negative dependence, and is also frequent under very strong positive dependence.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/alt_normal}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_g}
\end{figure}
\jy{Watch for missing figure labels}

@@

We evaluated the size and power performance of the NPBB test under automatic
\jy{How was the block size set when the chosen one is as big as $n$?
  Excluded? Or settting it as the minimum of the auto-selected and $\sqrt{n}$?}
block length selection by restricting attention to those replicates where
the selected block size was $\sqrt{n}$ or lower. The size performane is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Under this restriction, the method with block size selected by
\citet{politis2004automatic} maintains reasonable size for moderately positively
dependent series. However, for $|\tau| > 0.5$, neither the automatic selection
\jy{refer to Figures 1-2}
nor the cubic root setting holds its size. The power results are shown in
Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, the two settings exhibit
\jy{comparing with the power figure in the simulation section. Right? Clarify.}
comparable power, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citet{politis2004automatic}
performs reasonably well in some settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more challenging.

>>>>

Automatic block size selection tends to yield larger block sizes than our
fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
negative or very strong positive dependence it systematically produces
block sizes that are excessively large, sometimes as large as or larger
than $n$. Note that in our simulations, we set the block size to 
$\min \{n, \hat l\}$, where
$\hat l$ is the block size selected by \citet{politis2004automatic}'s
procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
showing the distribution of block sizes selected by \citet{politis2004automatic}
for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
block sizes exceeding $n$ across varying levels of dependence and sample sizes.
The selection of block sizes larger than $n$ occurs systematically under strong
negative dependence, and is also frequent under very strong positive dependence.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/alt_normal}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_g}
\end{figure}

@@

We evaluated the size and power performance of the NPBB test under automatic
\jy{How was the block size set when the chosen one is as big as $n$?
  Excluded? Or settting it as the minimum of the auto-selected and $\sqrt{n}$?}
\mc{the block size was set to $n$, I added a sentence in the previous paragraph}
block length selection by restricting attention to those replicates where
the selected block size was $\sqrt{n}$ or lower. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Under this restriction, the method with block size selected by
\citet{politis2004automatic} maintains reasonable size for moderately positively
dependent series. However, for $|\tau| > 0.5$, neither the automatic selection
\jy{refer to Figures 1-2}
\mc{addressed}
nor the cubic root setting (as shown in Figures~\ref{fig:qq_n} and 
\ref{fig:qq_g}) holds its size. The power results are shown in
Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, when comparing 
with Figure~\ref{fig:rr}, the two settings exhibit
\jy{comparing with the power figure in the simulation section. Right? Clarify.}
\mc{addressed}
similar power, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citet{politis2004automatic}
performs reasonably well in some settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more challenging.
